---
title: '210921-notes'
author: H
date: '2021-09-21'
slug: Notes
categories:
  - Programming notes
tags:
  - data science
---

# Chapter 7: model

1. *optim()* : minimize the value via changing arguments
1. *coef(lm_model)* : show the coefficients (slop and intercept)
1. *data_grid()* : generate the unique varables 
1. *add_prediction()* : generate the pred and add a column to data frame 
  *plot prediction and actual point to demonstrate the model
1. *add_residuals()* : generate the residual and add a column to data frame
  plot the residuals with *geom_freqpoly()*  vs *geom_histogram()* <br />
  equal to *line* vs *barchat* <br />
  **the average of the residual will always be 0** <br />
  or plot x against residuals : it should look like random noise<br />
(**note** : data should set up clearly x and y variable)<br />


**R in Data Science** : p353 <br />
Excercises<br />
1. the residual distance largely vary. <br />
see *dis*
```{r, message=F}
library(tibble)
library(tidyverse)
library(kableExtra)
dis <- list()
for(i in 1:10){
sim1a <- tibble(
  x=rep(1:10,each=3),
  y=x*1.5+6+rt(length(x),df=2)
)
dis[i] <- round(sqrt(mean((summary(lm(y~x,data=sim1a))$residuals)^2)),5)
}
dis <- do.call(rbind.data.frame,dis)
colnames(dis) <- 'distance'
dis %>% 
  kbl() %>% 
  kable_paper('hover',full_width=F)

sim1a %>% ggplot(aes(x=x,y=y))+
  geom_point()+
  geom_abline(aes(intercept=coef(lm(y~x,data=sim1a))[[1]],slope=coef(lm(y~x,data=sim1a))[[2]]))

```

2. Other distance measure : mean-absolute distance.
 instead of root-mean distance
```{r eval=TRUE}
lm_sim1a <- lm(y~x,data=sim1a)
sim1a <- as.data.frame(sim1a)
model1 <- function(a,data){ a[1]+ data$x*a[2]}
measure_dis <- function(mod,data) {
  new <- data %>% select(x)
  diff <- data$y-model1(mod,new)
  mean(abs(diff))
}
measure_dis(c(1,2),sim1a)
best <- optim(c(0,0),measure_dis,data=sim1a)
# the difference between abs-mean = best$par and root-mean =coef(lm)
best$par #a1 =intercept, a2 =slope
coef(lm_sim1a)
```
error and solution : 
*prediction : predict() 
[AWS](https://statisticsglobe.com/error-in-model-frame-default-must-be-data-frame-in-r)

3. three-parameter model : a1 + data$x*a2 + a3 <br />
a1 and a3 should combine into one parameter ? 


**R in Data Science** : p358 <br />
Exercise <br />
1. lm() ->> loess() : fit a smooth curve
```{r}
library(modelr)
model_loess <- loess(y~x, data =sim1)
grid <-  sim1 %>% data_grid(x) %>% add_predictions(model_loess)
sim1 %>% ggplot(aes(x,y))+
  geom_point()+
  geom_line(aes(x,pred),data=grid)+
  ggtitle('loess regression line')+
  NULL
sim1 <- sim1 %>% add_residuals(model_loess)
sim1 %>% ggplot(aes(resid))+
  geom_freqpoly()
sim1 %>% ggplot(aes(x,resid))+
  geom_point()+
  geom_ref_line(h=0)
```

2. *add_predictions*, *gather_predictions*, *spread_predictions*                              <br />
  The difference between these three similar functions                                        <br />
  *add_predictions* : add a new column to origin data frame named as 'pred'                   <br />
  *gather_predictions* : add two columns to origin data frame, which are 'model' and 'pred'   <br />
  *spread_predictions* : add a new column to origin data frame named as 'model_name'          <br />
  
3. *geom_ref_line()* from modelr package
   the ref in 0 is easy to see the difference
   
4. abs residual 
  

