---
title: '210921-notes'
author: H
date: '2021-09-21'
slug: Notes
categories:
  - Programming notes
tags:
  - data science
---
1. *optim()* : minimize the value via changing arguments
1. *coef(lm_model)* : show the coefficients (slop and intercept)



**R in Data Science** : p353 <br />
Excercises<br />
1. the residual distance largely vary.
see *dis*
```{r, message=F}
library(tibble)
library(tidyverse)
library(kableExtra)
dis <- list()
for(i in 1:10){
sim1a <- tibble(
  x=rep(1:10,each=3),
  y=x*1.5+6+rt(length(x),df=2)
)
dis[i] <- round(sqrt(mean((summary(lm(y~x,data=sim1a))$residuals)^2)),5)
}
dis <- do.call(rbind.data.frame,dis)
colnames(dis) <- 'distance'
dis %>% 
  kbl() %>% 
  kable_paper('hover',full_width=F)

sim1a %>% ggplot(aes(x=x,y=y))+
  geom_point()+
  geom_abline(aes(intercept=coef(lm(y~x,data=sim1a))[[1]],slope=coef(lm(y~x,data=sim1a))[[2]]))

```

2. Other distance measure : mean-absolute distance.
 instead of root-mean distance
```{r eval=TRUE}
lm_sim1a <- lm(y~x,data=sim1a)
sim1a <- as.data.frame(sim1a)
model1 <- function(a,data){ a[1]+ data$x*a[2]}
measure_dis <- function(mod,data) {
  new <- data %>% select(x)
  diff <- data$y-model1(mod,new)
  mean(abs(diff))
}
measure_dis(c(1,2),sim1a)
best <- optim(c(0,0),measure_dis,data=sim1a)
# the difference between abs-mean = best$par and root-mean =coef(lm)
best$par #a1 =intercept, a2 =slope
coef(lm_sim1a)
```
error and solution : 
*prediction : predict() 
[AWS](https://statisticsglobe.com/error-in-model-frame-default-must-be-data-frame-in-r)

3. three-parameter model : a1 + data$x*a2 + a3 <br />
a1 and a3 should combine into one parameter ? 





